Insert here, the title of your paper, Capitalize first letter

### 2022-10-26 src/Paper.tex
use our bibliography

 \begin{thebibliography}{}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

\bibitem{Massimo2011}
{F}ilippini, Massimo, and Lester C. Hunt. (2011) ``Energy demand and
energy efficiency in the OECD countries: a stochastic demand frontier
approach." {\it Energy Journal} {\bf 32} (2): 59--80.
\bibitem{Massimo2012}
Filippini, Massimo, and Lester C. Hunt. (2012) ``US residential
energy demand and energy efficiency: A stochastic demand frontier
approach." {\it Energy Economics} {\bf 34} (5): 1484--1491.
\bibitem{Thomas2015} 
Weyman-Jones, Thomas, J\'{u}lia Mendon\c{c}a Boucinha, and Catarina
Feteira In\'{a}cio. (2015) ``Measuring electric energy efficiency in
Portuguese households: a tool for energy policy." {\it Management of Environmental Quality: An International Journal} {\bf 26} (3): 407--422.
\bibitem{} 
Saunders, Harry (2009) ``Theoretical Foundations of the Rebound Effect'', in Joanne Evans and Lester Hunt (eds) {\it International Handbook on the Economics of Energy}, Cheltenham, Edward Elgar
\bibitem{} 
Sorrell, Steve (2009) ``The Rebound Effect: definition and estimation'', in Joanne Evans and Lester Hunt (eds) {\it International Handbook on the Economics of Energy}, Cheltenham, Edward Elgar 
 \end{thebibliography}

@@

>>>>

@@

\section{Acknowledgements}
This research was funded in part by the German Federal Ministry of Transport and Digital Infrastructure (funding number 16AVF2160)

\bibliography{bibliography}
\bibliographystyle{../src/elsarticle-harv}
